linguistic_analysis_C-D.Rmd : Linguistic quantity and complexity

### 2021-06-07 code/linguistic_analysis_C-D.Rmd
trialNum

---
title: "linguistic_analysis_C.Rmd : Linguistic quantity and complexity"
output: html_document
---

@@

ggplot(d_flowers_utt_length, aes(x=repNum, y=total_num_words, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,50))+
  labs(title="Number of words", y="Number of words", x="Round number", color="playerId")+
  theme(legend.position="bottom")
```

@@

ggplot(d_flowers_n_turns, aes(x=repNum, y=n, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Round number", color="playerId")+
  theme(legend.position="bottom")

```{r number_of_turns2}
## 2b. Number of turns
d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(playerId, repNum, gameId, blockNum) %>%
  summarise(n_utt_speaker=n())

ggplot(d_flowers_n_utt_speaker, 
       aes(x=repNum, y=n_utt_speaker, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_wrap(~playerId, nrow=1)+
  xlab("Round number") + 
  ylab("Number of turns") + 
  theme_bw()
```

@@

ggplot(d_flowers_pos, 
       aes(x=repNum, y=prop_pos, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_wrap(~pos, nrow=1)+
  xlab("Round number") + 
  ylab("Proportion of pos") + 
  theme_bw()

@@

##STEP FOUR - Feedback items and markers

@@

d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(playerId, repNum, gameId, blockNum) %>%
  summarise(n_utt_speaker=n())

d_flowers_n_utt_game <- d_flowers %>%
  group_by(repNum, gameId, blockNum) %>%
  summarise(n_utt_game=n())

@@

ggplot(d_flowers_n_utt_dist, 
       aes(x=repNum, y=overall_turns, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_wrap(~playerId, nrow=1)+
  xlab("Round number") + 
  ylab("Proportion of turns") + 
  theme_bw()

@@

d_flowers_q <- d_flowers %>% 
 mutate(sentence_type = ifelse(str_detect(text, "\\?"), 
                             "question",
                             "other")) %>%
 group_by(playerId, repNum, gameId, blockNum, sentence_type) %>%
 summarise(n_sentence_Type=n()) %>%
 filter(sentence_type=="question") %>%
 left_join(d_flowers_n_utt_speaker) %>%
 mutate(prop_questions = n_sentence_Type/n_utt_speaker )

ggplot(d_flowers_q, 
       aes(x=repNum, y=prop_questions, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  xlab("Round number") + 
  ylab("Proportion of questions") + 
  theme_bw()

>>>>

---
title: "linguistic_analysis_C-D.Rmd : Linguistic quantity and complexity"
output: html_document
---

@@

ggplot(d_flowers_utt_length, aes(x=trialNum, y=total_num_words, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  facet_wrap(~gameId, nrow=1) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,50))+
  labs(title="Number of words", y="Number of words", x="Round number", color="playerId")+
  theme(legend.position="bottom")
```

@@

ggplot(d_flowers_n_turns, aes(x=trialNum, y=n, color=as.factor(playerId)))+
  facet_wrap(~gameId, nrow=1) +
  scale_color_brewer(palette="Dark2")+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Round number", color="playerId")+
  theme(legend.position="bottom")

```
### 2b. Number of turns
```{r number_of_turns2}

d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(playerId, trialNum, gameId, blockNum) %>%
  summarise(n_utt_speaker=n())

ggplot(d_flowers_n_utt_speaker, 
       aes(x=trialNum, y=n_utt_speaker, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_wrap(~ playerId) +
  xlab("Round number") + 
  ylab("Number of turns") + 
  theme_bw()
```

@@

ggplot(d_flowers_pos, 
       aes(x=trialNum, y=prop_pos, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_wrap(~pos, nrow=1)+
  xlab("Round number") + 
  ylab("Proportion of pos") + 
  theme_bw()

@@

## STEP FOUR - Feedback items and markers

@@

d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(playerId, trialNum, gameId, blockNum) %>%
  summarise(n_utt_speaker=n())

d_flowers_n_utt_game <- d_flowers %>%
  group_by(trialNum, gameId, blockNum) %>%
  summarise(n_utt_game=n())

@@

#ggplot(d_flowers_n_utt_dist, 
#       aes(x=trialNum, y=overall_turns, label=playerId)) + 
#  geom_smooth(method = "lm", formula = y~x) + 
#  geom_point(alpha=.1) +
#  facet_wrap(~playerId)+
#  xlab("Round number") + 
#  ylab("Proportion of turns") + 
#  theme_bw()

@@

d_flowers_n_utt_speaker <- d_flowers %>%
  group_by(playerId, trialNum, gameId, blockNum) %>%
  summarise(n_utt_speaker=n())

d_flowers_q <- d_flowers %>% 
 mutate(sentence_type = ifelse(str_detect(text, "\\?"), 
                             "question",
                             "other")) %>%
 group_by(playerId, trialNum, gameId, blockNum, sentence_type) %>%
 summarise(n_sentence_Type=n()) %>%
 filter(sentence_type=="question") %>%
 left_join(d_flowers_n_utt_speaker) %>%
 mutate(prop_questions = n_sentence_Type/n_utt_speaker )

ggplot(d_flowers_q, 
       aes(x=trialNum, y=prop_questions, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  facet_wrap(~ playerId) +
  geom_point(alpha=.1) +
  xlab("Round number") + 
  ylab("Proportion of questions") + 
  theme_bw()
